Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-12-01 cbm-rbd-paper.tex
abstract and keywords for submission

\begin{abstract}
We propose a new condition-based maintenance policy for complex systems,
based on the status (working, defective) of all components within a system,
as well as the relaibility block diagaram of the system.
%
By means of the survival signature,
a generalization of the system signature allowing for multiple component types,
we obtain a predictive distribution for the system survival time,
%(also known as RUL, remaining useful life)
also known as residual life distribution,
based on which of the system's components currently function or not,
and the current age of the functioning components.

>>>>

\begin{abstract}
We propose a new condition-based maintenance policy for complex systems,
based on the status (working, defective) of all components within a system,
as well as the reliability block diagaram of the system.
%
By means of the survival signature,
a generalization of the system signature allowing for multiple component types,
we obtain a predictive distribution for the system survival time,
%(also known as RUL, remaining useful life)
also known as residual life distribution,
based on which of the system's components currently function or not,
and the current age of the functioning components.
